Diffusion Models for Tissues and Tumor Growth

### 2024-03-17 paper.tex
Fixing typos

\begin{enumerate}
    \item[(i)] The tumor is a sphere with perfect symmetry at all times, leaving the experiment to have 2 independent variables: time, $t$, and $r$, the radial distance.
    \item[(ii)] Cancer cells die when the nutrient levels, $\sigma(r, t)$ drop below a critical minimum of $\sigma_{min}.$ Oxygen is the most essential nutirient and is modeled using the methods described in the paper by Hill (1928).
    \item[(iii)] Oxygen is used by living cells only and depends on the nutrient concentration.
\end{enumerate}

@@

\begin{enumerate}
    \item[(i)] All living tumor cells are the same and do not fluctuate in size.
    \item[(ii)] Mitosis occurs instantaniously and all new cells are the same size as existing cells.
    \item[(iii)] The growth rate via mitosis is a distribution $S(\sigma, \beta)$ with $S(\sigma, \beta) = 0$ for $\beta > \beta_{max}$ or $\sigma < \sigma_{min}$.
    \item[(iv)] The core loses cell volume proportional to its volume with the proportionality constant defined as $3\lambda$.
\end{enumerate}

@@

Using our assumption that the necrotic core loses volume at a constant rate, we can proudce the integral

>>>>

\begin{enumerate}
    \item[(i)] The tumor is a sphere with perfect symmetry at all times, leaving the experiment to have 2 independent variables: time, $t$, and $r$, the radial distance.
    \item[(ii)] Cancer cells die when the nutrient levels, $\sigma(r, t)$ drop below a critical minimum of $\sigma_{min}.$ Oxygen is the most essential nutrient and is modeled using the methods described in the paper by Hill (1928).
    \item[(iii)] Oxygen is used by living cells only and depends on the nutrient concentration.
\end{enumerate}

@@

\begin{enumerate}
    \item[(i)] All living tumor cells are the same and do not fluctuate in size.
    \item[(ii)] Mitosis occurs instantaneously and all new cells are the same size as existing cells.
    \item[(iii)] The growth rate via mitosis is a distribution $S(\sigma, \beta)$ with $S(\sigma, \beta) = 0$ for $\beta > \beta_{max}$ or $\sigma < \sigma_{min}$.
    \item[(iv)] The core loses cell volume proportional to its volume with the proportionality constant defined as $3\lambda$.
\end{enumerate}

@@

Using our assumption that the necrotic core loses volume at a constant rate, we can derive the integral
